---
title: "Encrypted document test"
author: "Richard D. Morey"
date: "`r Sys.Date()`"
output: encryptRmd::html_document_enc

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## MathJax content

Entering the key `key1` will reveal the encrypted equation.

```{r}
r"(
\[
f(x) = \frac{1}{\sqrt{2\pi\sigma^2}}\exp\left\{-\frac{1}{2\sigma^2}(x - \mu)^2\right\}
\]
)" |>
  encryptRmd::encrypt_content_html(key = 'key1', mathjax = TRUE, character = FALSE, protect = FALSE)
```


## An encrypted gt table

Entering the key `key2` will reveal the encrypted `gt` table.

```{r}
gt::gt(sleep) |>
  gt::as_raw_html() |>
  encryptRmd::encrypt_content_html(key = 'key2', character = FALSE, protect = FALSE)
```

## Executing javascript on the result

Entering the key `key3` will reveal the blinking text. When it is revealed, the listener for the `decrypted` event defined below is triggered, and the text is made to blink. This can be used to (e.g.) provide syntax highlighting or other post-processing tasks. The chunk is set to `echo=TRUE` for demonstration; in practice, you'd probably want to set `echo=FALSE`.

The `decrypted` event is fired after markdown and MathJax processing is complete.


```{js echo=TRUE}
window.addEventListener('decrypted', function(e){
  const el = $(e.target).find('#blinking');
  
  setInterval(()=>{
    el.fadeOut(500).fadeIn(500);
  }, 1000)
});

```


```{r}
'<p id="blinking">This text should be made to blink.</p>' |>
    encryptRmd::encrypt_content_html(key = 'key3', character = FALSE, protect = FALSE)
```

